install.packages("pacman")

require(pacman)  # Gives a confirmation message.
library(pacman)  # No message.



pacman::p_load(pacman, dplyr, tidyr, stringr, ggplot2, rmarkdown, odbc, DBI, tidyverse, kableExtra) 


knitr::opts_chunk$set(message=F,
                      warning=F,
                      fig.width=6, 
                      fig.height=3)
                      


```{r db_connection}
myconn <- DBI::dbConnect(drv = odbc::odbc(),
                         dsn = Sys.getenv("ODBC_DSN_NAME"),
                         uid = Sys.getenv("SNOWFLAKE_USER"), # yozzzu may also leave the user_id empty if using Shibboleth
                         pwd = Sys.getenv("SNOWFLAKE_PWD")   # you may also leave the password empty if using Shibboleth
                         )
```

data<-dbGetQuery(myconn,
                 "select * from HRM_INIT")
                 
``` {r}
ggplot(data=data,aes(x=RACE)) +
  geom_bar()
  
```


``` {r}
ggplot(data %>% group_by(SEX) %>%
         dplyr::summarize(freq=n()) %>% ungroup, 
       aes(x="",y=freq,fill=SEX)) +
  geom_bar(width=1,stat="identity")+
  coord_polar("y", start=0)+
  labs(x="",y="")
  
```
```{r}
#summary descriptive stat TOTAL_MEDICATION_TYPE
summary(data$TOTAL_MEDICATION_TYPE)
```
```{r}
#summary descriptive stat DEATH_AFTER_FIRST_DOSE
ggplot(data %>% group_by(IS_DEAD) %>%
         dplyr::summarize(freq=n()) %>% ungroup, 
       aes(x="",y=freq,fill=IS_DEAD)) +
  geom_bar(width=1,stat="identity")+
  coord_polar("y", start=0)+
  labs(x="",y="")
```

```{r}
#summary descriptive stat DEATH_AFTER_FIRST_DOSE
aset<-data[data$IS_DEAD == '1' & data$DEATH_AFTER_FIRST_DOSE >= 0,] 
summary(aset$DEATH_AFTER_FIRST_DOSE)
```